Weighted Model Counting with Conditional Probabilities

### 2020-07-19 paper.tex
A detailed example

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[UKenglish]{babel}
\usepackage[UKenglish]{isodate}
\usepackage{fullpage}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{hyperref}
\usepackage[capitalise]{cleveref}
\usepackage{bm}
\usepackage{booktabs}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[backgroundcolor=lightgray]{todonotes}
\usepackage{complexity}
\usepackage{soul}
\usepackage[ruled,vlined]{algorithm2e}

@@

\item Describe the changes to the Cachet DIMACS CNF format (and mention that, if
  needed, the assumption that $\Pr(A) + \Pr(\neg A) = 1$ can be discarded).
  Instead of \texttt{w 1 0.1}, we have \texttt{w 1 2 0.1} and \texttt{w 1 -2
    0.5}. This provides half of the information; the remaining half can be
  deduced, but the algorithm itself can support weights that are not necessarily
  probabilities. Ditto for non-binary values (the shorter version).
\item Give some examples (and/or a proof) of why this is correct when combined
  with arbitrary clauses (i.e., conjunctions of disjunctions).

@@

\item Add a mini theorem: my model can express any probability distribution on
  the BA (just like BNs can express any discrete distribution).

@@

\item Decide on terminology: coproducts/pushouts vs (amalgamated) free products.
  Probably the former.

@@

\item There is a new version of ADDMC.
\item Prove that we have an algebra of functions with one additional operation.

@@

\item Show how the $\phi$ from the algorithm can be encoded in the typical
  DIMACS CNF format.

@@

@@

\begin{definition}[Operations on functions]
  Let $A\colon 2^X \to [0, 1]$ and $B\colon 2^Y \to [0, 1]$ be Boolean
  functions, $\alpha \in [0, 1]$, and $x \in X$. We define the following
  operations:
  \begin{description}
  \item[Addition:] $A+B$ is a function $A+B\colon 2^{X \cup Y} \to [0, 1]$ such
    that
    \[
      (A+B)(\tau) = A(\tau \cap X) + B(\tau \cap Y)
    \]
    for all $\tau \in 2^{X \cup Y}$.
  \item[Inverse:] $\overline{A}$ is a function $\overline{A}\colon 2^X \to [0,
    1]$ such that
    \[
      \overline{A}(\tau) = 1 - A(\tau)
    \]
    for all $\tau \in 2^X$.
  \item[Multiplication:] $A \cdot B$ is a function $A \cdot B\colon 2^{X \cup Y}
    \to [0, 1]$ such that
    \[
      (A \cdot B)(\tau) = A(\tau \cap X) \cdot B(\tau \cap Y)
    \]
    for all $\tau \in 2^{X \cup Y}$.
  \item[Scalar multiplication:] $\alpha A$ is a function $\alpha A\colon 2^X \to
    [0, 1]$ such that
    \[
      (\alpha A)(\tau) = \alpha \cdot A(\tau)
    \]
    for all $\tau \in 2^X$.
  \item[Projection:] $\exists_xA$ is a function $\exists_xA\colon 2^{X \setminus
      \{ x \}} \to [0, 1]$ such that
    \[
      (\exists_xA)(\tau) = A(\tau) + A(\tau \cup \{ x \})
    \]
    for all $\tau \in 2^{X \setminus \{x \}}$.
  \end{description}
\end{definition}
\begin{remark}
  Note that $A + \overline{A} = 1$.
\end{remark}

\begin{definition}[Special functions]
  \phantom{}
  \begin{itemize}
  \item unit $1\colon 2^\emptyset \to [0, 1]$, $1(\tau) = 1$.
  \item zero $0\colon 2^\emptyset \to [0, 1]$, $0(\tau) = 0$.
  \item constant $[a]\colon 2^{\{a\}} \to [0, 1]$,
    \[
      [a](\tau) =
      \begin{cases}
        1 & \text{if } a \in \tau \\
        0 & \text{if } a \not\in \tau.
      \end{cases}
    \]
  \end{itemize}
\end{definition}

\begin{algorithm}
  $\phi \gets 1$\;
  \For{$X \in V$}{
    \textit{let} $\mathrm{pa}(X) = \{ Y_1, \dots, Y_n \}$\;
    \eIf{$|\im X| = 2$}{
      \For{$(y_1, \dots, y_n) \in \prod_{i = 1}^n \im Y_i$}{
        $p_1 \gets \Pr(X = 1 \mid Y_1 = y_1, \dots, Y_n = y_n)$\;
        $p_0 \gets \Pr(X \ne 1 \mid Y_1 = y_1, \dots, Y_n = y_n)$\;
        $\phi \gets \phi \cdot \left( p_1[\lambda_{X=1}] \cdot \prod_{i=1}^n
          [\lambda_{Y_i=y_i}] + p_0 \overline{[\lambda_{X=1}]} \cdot
          \prod_{i=1}^n [\lambda_{Y_i=y_i}] \right)$\;
      }
    }{
      \textit{let} $\im X = \{ x_1, \dots, x_m \}$\;
      $\phi \gets \phi \cdot \left( \sum_{i=1}^m [\lambda_{X = x_i}] \right)
      \cdot \prod_{i=1}^m \prod_{j=i+1}^m (\overline{[\lambda_{X = x_i}]} +
      \overline{[\lambda_{X = x_j}]})$\;
      \For{$x \in \im X$ {\rm \textbf{and}} $(y_1, \dots, y_n) \in \prod_{i = 1}^n \im
        Y_i$}{
        $p_x \gets \Pr(X = x \mid Y_1 = y_1, \dots, Y_n = y_n)$\;
        $\phi \gets \phi \cdot \left( p_x[\lambda_{X=x}] \cdot \prod_{i=1}^n
          [\lambda_{Y_i=y_i}] + \overline{[\lambda_{X=1}]} \cdot \prod_{i=1}^n
          [\lambda_{Y_i=y_i}] \right)$\;
      }
    }
  }
  \Return{$\phi$}\;
\end{algorithm}

\begin{lemma} \label{lemma:cpt}
  Let $X \in V$ be a random variable with $\mathrm{pa}(X) = \{ Y_1, \dots, Y_n
  \}$. Then the iteration of the main loop of the algorithm (when run on $X$)
  multiplies $\phi$ by a function $\mathrm{CPT}_X\colon 2^{E^*(X)} \to [0, 1]$
  such that
  \[
    \mathrm{CPT}_X(\tau) =
    \begin{cases}
      \Pr(X = x \mid Y_1 = y_1, \dots, Y_n = y_n) &
      \begin{aligned}
        &\text{if } \textstyle \tau = \lambda_{X=x} \land \bigwedge_{i=1}^n
        \lambda_{Y_i=y_i} \\
        &\text{for some } \textstyle (x, y_1, \dots, y_n) \in \im X \times
        \prod_{i=1}^n \im Y_i
        \end{aligned} \\
      0 & \text{otherwise.}
    \end{cases}
  \]
  for all $\tau \in 2^{E^*(X)}$.
\end{lemma}
\begin{proof}
\end{proof}

\begin{proposition} \label{lemma:full_distribution}
  $\prod_{X \in V} \mathrm{CPT}_X\colon 2^U \to [0, 1]$ represents the full
  probability distribution of the Bayesian network, i.e., if $V = \{ X_1, \dots,
  X_n\}$, then
  \[
    \left( \prod_{X \in V} \mathrm{CPT}_X \right)(\tau) =
    \begin{cases}
      \Pr(X_1 = x_1, \dots, X_n = x_n) & \text{if } \tau = \bigwedge_{i=1}^n
      \lambda_{X_i = x_i} \text{ for some } (x_1, \dots, x_n) \in \prod_{i=1}^n
      \im X_i \\
      0 & \text{otherwise,}
    \end{cases}
  \]
  for all $\tau \in 2^U$.
\end{proposition}
\begin{proof}
  We have that
  \[
    \left( \prod_{X \in V} \mathrm{CPT}_X \right)(\tau) = \prod_{X \in V}
    \mathrm{CPT}_X(\tau \cap E^*(X)).
  \]
  If $\mathrm{CPT}_X(\tau \cap E^*(X)) = 0$ for some $X \in V$, then $\left(
    \prod_{X \in V} \mathrm{CPT}_X \right)(\tau) = 0$. Otherwise, for each $X
  \in V$, $\tau \cap E^*(X)$ can be expressed as a conjunction of indicator
  variables. Moreover, those indicator variables must match, i.e.,
  \[
    \tau = \bigwedge_{X \in V} \lambda_{X = v_X}
  \]
  for some $(v_X)_{X \in V} \in \prod_{X \in V} \im X$. Then, by
  \cref{lemma:cpt},
  \[
    \left( \prod_{X \in V} \mathrm{CPT}_X \right)(\tau) = \prod_{X \in V} \Pr
    \left( X=v_X \;\middle|\; \bigwedge_{Y \in \mathrm{pa}(X)} Y=v_Y \right) =
    \Pr \left( \bigwedge_{X \in V} X=v_X \right),
  \]
  where the last step follows from the definition of a Bayesian network.
\end{proof}

\begin{theorem}
  Let $\phi\colon 2^U \to [0, 1]$ be a function generated by the algorithm. Then
  \[
    (\exists_U(\phi \cdot [\lambda_{X=x}]))(\emptyset) = \Pr(X = x).
  \]
\end{theorem}
\begin{proof}
  Let $V = \{ X, Y_1, \dots, Y_n \}$. Then
  \begin{align*}
    (\exists_U (\phi \cdot [\lambda_{X=x}]))(\emptyset) &= \sum_{\tau \in 2^U} (\phi \cdot [\lambda_{X=x}])(\tau) = \sum_{\lambda_{X=x} \in \tau \in 2^U} \phi(\tau) = \sum_{\lambda_{X=x} \in \tau \in 2^U} \left( \prod_{Y \in V} \mathrm{CPT}_Y \right)(\tau) \\
    &= \sum_{(y_1, \dots, y_n) \in \prod_{i=1}^n \im Y_i} \Pr(X = x, Y_1 = y_1, \dots, Y_n = y_n) = \Pr(X = x)
  \end{align*}
  by the following arguments:
  \begin{itemize}
  \item the proof of Theorem~1 in the ADDMC paper \cite{DBLP:conf/aaai/DudekPV20};
  \item if $\lambda_{X=x} \not\in \tau \in 2^U$, then $(\phi \cdot
    [\lambda_{X=x}])(\tau) = \phi(\tau) \cdot [\lambda_{X=x}](\tau \cap \{
    \lambda_{X=x} \}) = \phi(\tau) \cdot 0 = 0$;
  \item \cref{lemma:full_distribution};
  \item marginalisation of a probability distribution.
  \end{itemize}
\end{proof}

% Acknowledgments. This work has made use of the resources provided by the
% Edinburgh Compute and Data Facility (ECDF) (http://www.ecdf.ed.ac.uk/).

>>>>

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[UKenglish]{babel}
\usepackage[UKenglish]{isodate}
\usepackage{fullpage}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{hyperref}
\usepackage[capitalise]{cleveref}
\usepackage{bm}
\usepackage{booktabs}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[backgroundcolor=lightgray]{todonotes}
\usepackage{complexity}
\usepackage{soul}
\usepackage[ruled,vlined]{algorithm2e}
\usepackage{subcaption}

@@

@@

@@

@@

\item Prove that we have an algebra of functions with two (?) additional
  operations. Or maybe just cite the original paper for this.

@@

\item Could clarify why $[\lambda_{X=0}] = \overline{[\lambda_{X=1}]}$. This
  follows from the definition. Or should I avoid the overline notation?
\item After the experiments are finished, note the processor, memory per thread,
  and add the following acknowledgment. This work has made use of the resources
  provided by the Edinburgh Compute and Data Facility (ECDF)
  (\url{http://www.ecdf.ed.ac.uk/}).

@@

\item Remark: for any function $A\colon 2^X \to \mathbb{R}_{\ge 0}$, $A +
  \overline{A} = 1$.

@@

\begin{definition}[Operations on functions]
  Let $A\colon 2^X \to \mathbb{R}_{\ge 0}$ and $B\colon 2^Y \to \mathbb{R}_{\ge
    0}$ be Boolean functions, $\alpha \in \mathbb{R}_{\ge 0}$, and $x \in X$. We
  define the following operations:
  \begin{description}
  \item[Addition:] $A+B$ is a function $A+B\colon 2^{X \cup Y} \to
    \mathbb{R}_{\ge 0}$ such that
    \[
      (A+B)(\tau) = A(\tau \cap X) + B(\tau \cap Y)
    \]
    for all $\tau \in 2^{X \cup Y}$.
  \item[Inverse:] $\overline{A}$ is a function $\overline{A}\colon 2^X \to
    \mathbb{R}_{\ge 0}$ such that
    \[
      \overline{A}(\tau) = 1 - A(\tau)
    \]
    for all $\tau \in 2^X$.
  \item[Multiplication:] $A \cdot B$ is a function $A \cdot B\colon 2^{X \cup Y}
    \to \mathbb{R}_{\ge 0}$ such that
    \[
      (A \cdot B)(\tau) = A(\tau \cap X) \cdot B(\tau \cap Y)
    \]
    for all $\tau \in 2^{X \cup Y}$.
  \item[Scalar multiplication:] $\alpha A$ is a function $\alpha A\colon 2^X \to
    \mathbb{R}_{\ge 0}$ such that
    \[
      (\alpha A)(\tau) = \alpha \cdot A(\tau)
    \]
    for all $\tau \in 2^X$.
  \item[Projection:] $\exists_xA$ is a function $\exists_xA\colon 2^{X \setminus
      \{ x \}} \to \mathbb{R}_{\ge 0}$ such that
    \[
      (\exists_xA)(\tau) = A(\tau) + A(\tau \cup \{ x \})
    \]
    for all $\tau \in 2^{X \setminus \{x \}}$.
  \end{description}
\end{definition}
Note that both addition and multiplication commute.

\begin{definition}[Special functions]
  \phantom{}
  \begin{itemize}
  \item unit $1\colon 2^\emptyset \to \mathbb{R}_{\ge 0}$, $1(\tau) = 1$.
  \item zero $0\colon 2^\emptyset \to \mathbb{R}_{\ge 0}$, $0(\tau) = 0$.
  \item constant $[a]\colon 2^{\{a\}} \to \mathbb{R}_{\ge 0}$,
    \[
      [a](\tau) =
      \begin{cases}
        1 & \text{if } a \in \tau \\
        0 & \text{if } a \not\in \tau.
      \end{cases}
    \]
  \end{itemize}
\end{definition}

Henceforth, for any function $A\colon 2^X \to \mathbb{R}_{\ge 0}$ and any set
$\tau$, we will write $A(\tau)$ to mean $A(\tau \cap X)$.

\begin{algorithm}
  $\phi \gets 1$\;
  \For{$X \in V$}{
    \textit{let} $\mathrm{pa}(X) = \{ Y_1, \dots, Y_n \}$\;
    $\mathrm{CPT}_X \gets 0$\;
    \eIf{$|\im X| = 2$}{
      \For{$(y_1, \dots, y_n) \in \prod_{i = 1}^n \im Y_i$}{
        $p_1 \gets \Pr(X = 1 \mid Y_1 = y_1, \dots, Y_n = y_n)$\;
        $p_0 \gets \Pr(X \ne 1 \mid Y_1 = y_1, \dots, Y_n = y_n)$\;
        $\mathrm{CPT}_X \gets \mathrm{CPT}_X + p_1[\lambda_{X=1}] \cdot
        \prod_{i=1}^n [\lambda_{Y_i=y_i}] + p_0 \overline{[\lambda_{X=1}]} \cdot
        \prod_{i=1}^n [\lambda_{Y_i=y_i}]$\;
      }
    }{
      \textit{let} $\im X = \{ x_1, \dots, x_m \}$\;
      \For{$x \in \im X$ {\rm \textbf{and}} $(y_1, \dots, y_n) \in \prod_{i =
          1}^n \im Y_i$}{
        $p_x \gets \Pr(X = x \mid Y_1 = y_1, \dots, Y_n = y_n)$\;
        $\mathrm{CPT}_X \gets \mathrm{CPT}_X + p_x[\lambda_{X=x}] \cdot
        \prod_{i=1}^n [\lambda_{Y_i=y_i}] + \overline{[\lambda_{X=1}]} \cdot
        \prod_{i=1}^n [\lambda_{Y_i=y_i}]$\;
      }
      $\mathrm{CPT}_X \gets \mathrm{CPT}_X \cdot \left( \sum_{i=1}^m [\lambda_{X
          = x_i}] \right) \cdot \prod_{i=1}^m \prod_{j=i+1}^m
      (\overline{[\lambda_{X = x_i}]} + \overline{[\lambda_{X = x_j}]})$\;
    }
    $\phi \gets \phi \cdot \mathrm{CPT}_X$\;
  }
  \Return{$\phi$}\;
\end{algorithm}

\begin{lemma} \label{lemma:cpt}
  Let $X \in V$ be a random variable with parents $\mathrm{pa}(X) = \{ Y_1,
  \dots, Y_n \}$. Then $\mathrm{CPT}_X\colon 2^{E^*(X)} \to \mathbb{R}_{\ge 0}$
  is such that for any $x \in \im X$ and $(y_1, \dots, y_n) \in \prod_{i=1}^n
  \im Y_i$,
  \[
    \mathrm{CPT}_X \left( \lambda_{X=x} \land \bigwedge_{i=1}^n
      \lambda_{Y_i=y_i} \right) = \Pr(X = x \mid Y_1 = y_1, \dots, Y_n = y_n).
  \]
\end{lemma}
\begin{proof}
  Let
  \[
    \tau = \lambda_{X=x} \land \bigwedge_{i=1}^n \lambda_{Y_i=y_i}.
  \]
  If $X$ is binary, then $\mathrm{CPT}_X$ is a sum of $2\prod_{i=1}^n |\im Y_i|$
  terms, one for each possible assignment of values to variables $X, Y_1, \dots,
  Y_n$. Exactly one of these terms is nonzero when applied to $\tau$, and it is
  equal to $\Pr(X = x \mid Y_1 = y_1, \dots, Y_n = y_n)$ by definition.

  If $X$ is not binary, then
  \[
    \left( \sum_{i=1}^m [\lambda_{X = x_i}] \right)(\tau) = 1,
  \]
  and
  \[
    \left( \prod_{i=1}^m \prod_{j=i+1}^m (\overline{[\lambda_{X = x_i}]} +
      \overline{[\lambda_{X = x_j}]}) \right)(\tau) = 1,
  \]
  so, by a similar argument as before,
  \[
    \mathrm{CPT}_X(\tau) = \Pr(X = x \mid Y_1 = y_1, \dots, Y_n = y_n).
  \]
\end{proof}

\begin{proposition} \label{lemma:full_distribution}
  $\phi\colon 2^U \to \mathbb{R}_{\ge 0}$ represents the full probability
  distribution of the Bayesian network, i.e., if $V = \{ X_1, \dots, X_n\}$,
  then
  \[
    \phi(\tau) =
    \begin{cases}
      \Pr(X_1 = x_1, \dots, X_n = x_n) & \text{if } \tau = \bigwedge_{i=1}^n
      \lambda_{X_i = x_i} \text{ for some } (x_1, \dots, x_n) \in \prod_{i=1}^n
      \im X_i \\
      0 & \text{otherwise,}
    \end{cases}
  \]
  for all $\tau \in 2^U$.
\end{proposition}
\begin{proof}
  If
  \[
    \tau = \bigwedge_{X \in V} \lambda_{X = v_X}
  \]
  for some $(v_X)_{X \in V} \in \prod_{X \in V} \im X$, then
  \[
    \phi(\tau) = \prod_{X \in V} \Pr \left( X=v_X \;\middle|\; \bigwedge_{Y \in
        \mathrm{pa}(X)} Y=v_Y \right) = \Pr \left( \bigwedge_{X \in V} X=v_X
    \right)
  \]
  by \cref{lemma:cpt} and the definition of a Bayesian network. Otherwise there
  must be some non-binary random variable $X \in V$ such that $|E(X) \cap \tau|
  \ne 1$. If $E(X) \cap \tau = \emptyset$, then
  \[
    \left( \sum_{i=1}^m [\lambda_{X = x_i}] \right)(\tau) = 0,
  \]
  and so $\mathrm{CPT}_X(\tau) = 0$, and $\phi(\tau) = 0$. If $|E(X) \cap
  \tau| > 1$, then we must have two different values $x_1, x_2 \in \im X$ such
  that $\{\lambda_{X=x_1}, \lambda_{X=x_2} \} \subseteq \tau$ which means that
  \[
    (\overline{[\lambda_{X=x_1}]} + \overline{[\lambda_{X=x_2}]})(\tau) = 0,
  \]
  and so, again, $\mathrm{CPT}_X(\tau) = 0$, and $\phi(\tau) = 0$.
\end{proof}

\begin{theorem}
  Let $\phi\colon 2^U \to \mathbb{R}_{\ge 0}$ be a function generated by the
  algorithm. Then
  \[
    (\exists_U(\phi \cdot [\lambda_{X=x}]))(\emptyset) = \Pr(X = x).
  \]
\end{theorem}
\begin{proof}
  Let $V = \{ X, Y_1, \dots, Y_n \}$. Then
  \begin{align*}
    (\exists_U (\phi \cdot [\lambda_{X=x}]))(\emptyset) &= \sum_{\tau \in 2^U} (\phi \cdot [\lambda_{X=x}])(\tau) = \sum_{\lambda_{X=x} \in \tau \in 2^U} \phi(\tau) = \sum_{\lambda_{X=x} \in \tau \in 2^U} \left( \prod_{Y \in V} \mathrm{CPT}_Y \right)(\tau) \\
    &= \sum_{(y_1, \dots, y_n) \in \prod_{i=1}^n \im Y_i} \Pr(X = x, Y_1 = y_1, \dots, Y_n = y_n) = \Pr(X = x)
  \end{align*}
  by the following arguments:
  \begin{itemize}
  \item the proof of Theorem~1 in the ADDMC paper \cite{DBLP:conf/aaai/DudekPV20};
  \item if $\lambda_{X=x} \not\in \tau \in 2^U$, then $(\phi \cdot
    [\lambda_{X=x}])(\tau) = \phi(\tau) \cdot [\lambda_{X=x}](\tau \cap \{
    \lambda_{X=x} \}) = \phi(\tau) \cdot 0 = 0$;
  \item \cref{lemma:full_distribution};
  \item marginalisation of a probability distribution.
  \end{itemize}
\end{proof}

\begin{example}
  \begin{figure}
    \centering
    \begin{subfigure}{0.2\textwidth}
      \centering
      \begin{tikzpicture}
        \node[latent] (W) {W};
        \node[latent, below right=of W] (T) {T};
        \node[latent, below left=of W] (F) {F};
        \edge {W} {F};
        \edge {W} {T};
      \end{tikzpicture}
    \end{subfigure}%
    \begin{subfigure}{0.8\textwidth}
      \centering
      \begin{tabular}[t]{cc}
        \toprule
        $w$ & $\Pr(W = w)$ \\
        \midrule
        1 & 0.5 \\
        0 & 0.5 \\
        \bottomrule
      \end{tabular}
      \begin{tabular}[t]{ccc}
        \toprule
        $w$ & $f$ & $\Pr(F = f \mid W = w)$ \\
        \midrule
        1 & 1 & 0.6 \\
        1 & 0 & 0.4 \\
        0 & 1 & 0.1 \\
        0 & 0 & 0.9 \\
        \bottomrule
      \end{tabular}
      \begin{tabular}[t]{ccc}
        \toprule
        $w$ & $t$ & $\Pr(T = t \mid W = w)$ \\
        \midrule
        1 & $l$ & 0.2 \\
        1 & $m$ & 0.4 \\
        1 & $h$ & 0.4 \\
        0 & $l$ & 0.6 \\
        0 & $m$ & 0.3 \\
        0 & $h$ & 0.1 \\
        \bottomrule
      \end{tabular}
    \end{subfigure}
    \caption{An example Bayesian network with its CPTs}
    \label{fig:example_bn}
  \end{figure}

  The Bayesian network in \cref{fig:example_bn} has
  \begin{align*}
    V &= \{ W, F, T \}, \\
    \mathrm{pa}(W) &= \emptyset, \\
    \mathrm{pa}(F) &= \mathrm{pa}(T) = \{ W \}, \\
    \im W &= \im F = \{ 0, 1 \}, \\
    \im T &= \{ l, m, h \}, \\
    E(W) &= \{ \lambda_{W=1} \}, \\
    E(F) &= \{ \lambda_{F=1} \}, \\
    E(T) &= \{ \lambda_{T=l}, \lambda_{T=m}, \lambda_{T=h} \}, \\
    E^*(W) &= \{ \lambda_{W=1} \}, \\
    E^*(F) &= \{ \lambda_{F=1}, \lambda_{W=1} \}, \\
    E^*(T) &= \{ \lambda_{T=l}, \lambda_{T=m}, \lambda_{T=h}, \lambda_{W=1} \}, \\
    \mathrm{CPT_W} &= 0.5[\lambda_{W=1}]+0.5\overline{[\lambda_{W=1}]} = 0.5 \cdot 1, \\
    \mathrm{CPT_F} &= 0.6[\lambda_{F=1}] \cdot [\lambda_{W=1}] + 0.4[\lambda_{F=0}] \cdot [\lambda_{W=1}] + 0.1[\lambda_{F=1}] \cdot [\lambda_{W=0}] + 0.9[\lambda_{F=0}] \cdot [\lambda_{W=0}] \\
      &= 0.6[\lambda_{F=1}] \cdot [\lambda_{W=1}] + 0.4\overline{[\lambda_{F=1}]} \cdot [\lambda_{W=1}] + 0.1[\lambda_{F=1}] \cdot \overline{[\lambda_{W=1}]} + 0.9\overline{[\lambda_{F=1}]} \cdot \overline{[\lambda_{W=1}]}, \\
    \mathrm{CPT_T} &= ([\lambda_{T=l}] + [\lambda_{T=m}] + [\lambda_{T=h}]) \cdot (\overline{[\lambda_{T=l}]} + \overline{[\lambda_{T=m}]}) \cdot (\overline{[\lambda_{T=l}]} + \overline{[\lambda_{T=h}]}) \cdot (\overline{[\lambda_{T=m}]} + \overline{[\lambda_{T=h}]}) \cdot (\dots),
  \end{align*}
  and can be encoded in a DIMACS-like CNF format as
  \[
    \begin{array}{l r r l l}
      \lambda\sb{T=l} &\lambda\sb{T=m} &\lambda\sb{T=h} & &0 \\
                      &-\lambda\sb{T=l} &-\lambda\sb{T=m} & &0 \\
                      &-\lambda\sb{T=l} &-\lambda\sb{T=h} & &0 \\
                      &-\lambda\sb{T=m} &-\lambda\sb{T=h} & &0 \\
      w &\lambda\sb{W=1} & &0.5 &0.5 \\
      w &\lambda\sb{F=1} &\lambda\sb{W=1} &0.6 &0.4 \\
      w &\lambda\sb{F=1} &-\lambda\sb{W=1} &0.1 &0.9 \\
      w &\lambda\sb{T=l} &\lambda\sb{W=1} &0.2 &1 \\
      w &\lambda\sb{T=m} &\lambda\sb{W=1} &0.4 &1 \\
      w &\lambda\sb{T=h} &\lambda\sb{W=1} &0.4 &1 \\
      w &\lambda\sb{T=l} &\lambda\sb{W=0} &0.6 &1 \\
      w &\lambda\sb{T=m} &\lambda\sb{W=0} &0.3 &1 \\
      w &\lambda\sb{T=h} &\lambda\sb{W=0} &0.1 &1
    \end{array}
  \]
  with each $\lambda$ replaced with a unique positive integer.
\end{example}
